\documentclass[11pt]{article} \usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper}
 
 
\title{SOAS Exchange App: Week 7 Update}
\author{Louis Fillo, John Hill & Gal Moore}
 
\begin{document}
\maketitle
 
\section{Progress overview}
In the previous two weeks we had a discussion on whether to use Xamarin
or Ionic as the framework to build our app. Upon reviewing the two options we
decided to go with Xamarin. The reasons are as follows:
 
\begin{itemize}
  \item The back end programming language is in C# which is very similar to Java
  \item Xamarin produces more powerful and faster apps than Ionic
  \item Xamarin has fantastic libraries supporting many funcionalities
\end{itemize}
 
We then started building the App in Xamarin with a learning by doing approach,
watching YouTube tutorials and reading online blogs to help us learn. We
created a GitHub repository such that we could share code and build and
maintain the same project. We have built various pages with some of the back end
functionality attached to it. Our next steps are to start building some of the
more complicated functionality and making the app look more presentable.
 
\section{Language Exchange App: Summary}
Facilitates the matching of users (predominantly SOAS students) for the purpose
of language exchange.  Language exchange involves two participants meeting up to
speak in languages that one side is a fluent/native speaker of, and the other
user is aiming to learn.  The exchange is reciprocal: exchangers swap roles.
The SOAS community covers a wide range of languages, so the app would need
features to match users who speak more obscure languages, as well as the major
languages.
 
\section{Individual actions/Completed Tasks}
 
\subsection{Gal Moore}
\begin{itemize}
   \item Connected to GitHub
   \item Got up to speed on Xamarin
   \item Playing around with Ionic, Angular & Cordova
\end{itemize}
 
\subsection{Louis Fillo}
\begin{itemize}
   \item Built settings page
   \item Wrote report
   \item Made changes to Github repository
\end{itemize}
 
\subsection{John Hill}
\begin{itemize}
   \item Got running on Xamarin
   \item Built login page and carousel page
   \item Set up GitHub repository
\end{itemize}
 
\section{Issues Encountered /& Next Steps}
\begin{itemize}
   \item Lots of issues setting up Xamarin
   \item Getting GitHub fully working was very time consuming
\end{itemize}
 
\begin{itemize}
   \item Start working on back end functionality like user authentication and
   chat functionality
   \item Start making the user experience more enjoyable
   \item Meeting IT teams from SOAS next week to discuss the back end server and
   show basic prototype
   \item Construct Gantt chart
   \item Investigate Shibboleth
\end{itemize}
 
\end{document}
\medskip